Source Summaries

### 2020-02-10 paper/sourceSummaries/summary2.tex
fixed my summary for week2

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{o'sullivan}

@@

\noindent
The main findings ot this paper present the vulnerabilities of the BD_ADDR field which is present in all BLE communication. O'Sullivan found that an attacker could use bluetooth fuzzing to determine the master source of a bluetooth connection and potentially forge a connection to it. Not to mention the fact that BD_ADDR's are not globally unique so an attacker could try to spoof their BD_ADDR until packets start flowing in.

>>>>

\bibentry{osullivan}

@@

\noindent
The main findings ot this paper present the vulnerabilities of the BD ADDR field which is present in all BLE communication. O'Sullivan found that an attacker could use bluetooth fuzzing to determine the master source of a bluetooth connection and potentially forge a connection to it. Not to mention the fact that BD ADDR's are not globally unique so an attacker could try to spoof their BD ADDR until packets start flowing in.
